### 2015-02-21 hmwkch5sol.tex
up to date with homeworks, i need to put lab assignments here too

%\includegraphics[width=2.5in]{hwk5jmpoutput.pdf}

%&
%\vspace{0.5in}
(6 pts)  We see that the distribution of body temperatures is unimodal and symmetric, with a general bell-shape to the histogram.  The points in the normal quantile plot generally follow the straight line in the plot. Due to the shape of the histogram and the straight line pattern in the normal quantile plot, it appears that the distribution of body temperatures in the sample can be modeled with the normal model.

>>>>

\centerline{\includegraphics[width=3in]{hmwkch5-histogram.pdf}\includegraphics[width=3in]{hmwkch5-normprob.pdf}}

\includegraphics[width=6in]{hmwkch5-summary.pdf}

%&
%\vspace{0.5in}
(6 pts)  We see that the distribution of body temperatures is unimodal and symmetric, with a general bell-shape to the histogram.  The points in the normal quantile plot generally follow the straight line in the plot. Due to the shape of the histogram and the straight line pattern in the normal quantile plot.  We can also count the number of observations that fall within 1, 2, and 3 standard deviations to compare against the 68-95-99.7 rule. These are 90, 
123, 129 which corresponds to 69-95-99.2, extremely close to the ideal.

It appears that the distribution of body temperatures in the sample can be modeled with the normal model.
